### 2016-03-08 Projects/DelCo_2014_2015/Reports/Hose_Stream_Report/TeX_Files/DelCo_Hose_Stream_Tests.tex
Some content added to conclusion section of hose stream report

Looking at Tests 16, 17, and 33 in Table~\ref{table:all_mon_vel_avgs}, the narrow and wide fog streams caused higher velocities when the flow path was fully established through the interior doorway compared to the straight stream. This trend is also observed in Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} above and Figs.~\ref{fig:Test_33_BDP_A6_Avg_All}~and~\ref{fig:Test_17_BDP_A10_Avg_All} in Appendix~\ref{sec:monitor_figs}. Additionally, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream. Finally, the Test 70 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_70_BDP_A10_Avg_All} suggest that a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle produce approximately the same amount of air movement through the interior doorway.
\FloatBarrier

@@

% --- STOPPED --- %

@@

**** Add more specific discussion of results ****

@@

>>>>

Looking at Tests 16, 17, and 33 in Table~\ref{table:all_mon_vel_avgs}, the narrow and wide fog streams caused higher velocities when the flow path was fully established through the interior doorway compared to the straight stream. This trend is also observed in Fig.~\ref{fig:Test_16_BDP_A10_Avg_All} above and Figs.~\ref{fig:Test_33_BDP_A6_Avg_All}~and~\ref{fig:Test_17_BDP_A10_Avg_All} in Appendix~\ref{chap:monitor_plots}. Additionally, the wide fog stream generally produced equal or higher air velocities compared to the narrow fog stream. Finally, the Test 70 results listed in Table~\ref{table:all_mon_vel_avgs} and plotted in Fig.~\ref{fig:Test_70_BDP_A10_Avg_All} suggest that a straight stream from a combination nozzle and a solid stream from a smooth bore nozzle produce approximately the same amount of air movement through the interior doorway.
\FloatBarrier

@@

@@

@@

A total of eight experiments were conducted to study the impact of different hose stream and application pattern combinations on air movement within residential scale structures.

Three experiments studied the differences between a straight stream, narrow fog stream, and wide fog stream emitted from a combination nozzle attached to a monitor aimed at specific locations in a structure for different ventilation configurations. For each of the three experiments, the average air velocity through the interior doorway while the flow path was fully established was greatest for the wide fog stream no matter the location and ventilation pattern within the structure. The magnitude of the average air velocity through the interior doorway while the flow path was fully established for the narrow fog stream was always equal to or greater than the magnitude of the average air velocity for the straight stream. Additionally, a fourth experiment using a monitor was conducted in which a straight stream from a combination nozzle was compared to a solid stream from a smooth bore nozzle aimed at a specified location for 60 seconds with a fully established flow path. The streams were compared for six different 60 seconds periods; three times for the monitor aimed at two locations. The results from the four monitor experiments suggest a wide fog stream impacts air movement within a structure the most out of any of the tested streams, followed by the narrow fog stream, and then the straight stream and solid stream from a smooth bore nozzle, which both caused approximately the same amount of air movement through the structure.

In addition to the monitor experiments, three different experiments were conducted using a handline to study the impact of different stream and application pattern combinations on air movement within a structure.
